Variation in gaze following across the life span: A process-level perspective

### 2024-05-21 paper/manuscript.Rmd
preprint after second revision

The idea of gaze as vector following has recently been introduced to the study of pointing gestures (@omadagain2019origin, see @li2023understanding for computational modeling). According to this hypothesis, when humans use pointing gestures, the index finger does not constitute "arrow" pointing at the target, but is used to touch the object within one's visual field. Consequently, the touch line is a vector that connects the eye and the pointed fingertip, and marks the object that the person's fingertip seems closest to touching from her perspective [@omadagain2019origin]. This supports the idea that vector estimation is relevant for social-cognitive abilities.

>>>>

The idea of gaze as vector following has recently been introduced to the study of pointing gestures (@omadagain2019origin, see @li2023understanding for computational modeling). According to this hypothesis, when humans use pointing gestures, the index finger does not constitute an "arrow" pointing at the target, but is used to touch the object within one's visual field. Consequently, the touch line is a vector that connects the eye and the pointed fingertip, and marks the object that the person's fingertip seems closest to touching from her perspective [@omadagain2019origin]. This supports the idea that vector estimation is relevant for social-cognitive abilities.
